Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-16 robdml.tex
tex

In most cases, our method outperforms the previous methods in every important
aspect, \ie, ERS, training cost (efficiency), and R@1, as shown in
\cref{tab:sota}.
%
HM[$\mathcal{R},\mathcal{M}$] and HM[$\mathcal{R},g_\mathsf{LGA}$] can reach a
higher ERS, but are excluded from comparison due to significant performance
drop in R@1.

It \emph{must} be acknowledged that the high R@1 performance of our method
largely stems from the source triplet sampling strategy, \ie, Softhard,
instead of our contribution.
%
But the other methods cannot reach the same level of robustness with the same
sampling strategy.
%
Besides, our method achieves the highest ERS at
the lowest R@1 drop under a fixed training cost.
%
Thus, our proposed method overwhelmingly outperforms the existing defenses
in overall performance.
%

>>>>

Our method overwhelmingly outperforms the previous methods in terms of the
overall performance. Namely, our method achieves the highest ERS with a very
low decrement in R@1 under a fixed training cost.
%
HM[$\mathcal{R},\mathcal{M}$] or HM[$\mathcal{R},g_\mathsf{LGA}$] can reach an
even higher ERS, but are excluded from comparison due to significant drop in
R@1.
%

It \emph{must} be acknowledged that the high R@1 performance of our method
largely stems from the source triplet sampling strategy, \ie, Softhard, instead
of our contribution.
%
Nevertheless, the state-of-the-art method, \ie, ACT could not reach the same
level of robustness with the same sampling strategy.
